Manuscript analyses

### 2025-06-13 cilta_cel/Manuscript analyses.Rmd
Update figure code for publication requirements

```{r Figure 2. Inflammatory markers after cilta-cel, fig.height=12}
LDH <- fig_dat %>% 
  select(pt_identifier, starts_with("ldh_")) %>% 
  pivot_longer(cols = -c(pt_identifier)) %>% 
  mutate(name = str_remove(name, "_k_ul|_k_u_l"),
         day = case_when(
           str_detect(name, "apheresis")            ~ "-28",
           str_detect(name, "pretreatment")         ~ "-28",
           str_detect(name, "day")                  ~ ((str_match(name, "([0-9]+)"))[,2])
         ), 
         day = case_when(
           day == 5                                 ~ "-5",
           TRUE                                     ~ day
         ),
         day = factor(day, levels = c("-28", "-5", "0", 
                                      "7", "14", "21", "30", "90", "180"))) %>% 
  ggplot(aes(x=day, y=value)) + 
  geom_boxplot() + 
  xlab("Days") + ylab("LDH represented with a log2 scale") + 
  theme_classic() + ggtitle("LDH") + 
  scale_y_continuous(trans = "log2") +
  stat_compare_means(label.x = 1.2 
                     # aes(label = paste0("p = ", ..p.format..))
  #                  aes(
  # label=ifelse(..p.format.. == 1e-04, "p<0.001", "Other")
  )

# cart1$`Ferritin day +7`[cart1$`Ferritin day +7`==">33511"] <- 33511
# cart1$`Ferritin day +7` <- as.numeric(cart1$`Ferritin day +7`)
Ferritin <- fig_dat %>% 
  select(pt_identifier, starts_with("ferritin_"), -ferritin_score) %>% 
  pivot_longer(cols = -c(pt_identifier)) %>% 
  mutate(name = str_remove(name, "_k_ul|_k_u_l"),
         day = case_when(
           str_detect(name, "apheresis")            ~ "-28",
           str_detect(name, "pretreatment")         ~ "-28",
           str_detect(name, "day")                  ~ ((str_match(name, "([0-9]+)"))[,2])
         ), 
         day = case_when(
           day == 5                                 ~ "-5",
           TRUE                                     ~ day
         ),
         day = factor(day, levels = c("-28", "-5", "0", 
                                      "7", "14", "21", "30", "90", "180"))) %>% 
  ggplot(aes(x=day, y=value)) + 
  geom_boxplot() + 
  xlab("Days") + ylab("Ferritin represented with a log2 scale") + 
  theme_classic() + ggtitle("Ferritin") + 
  scale_y_continuous(trans = "log2") +
  stat_compare_means(label.x = 1.2 
                     # aes(label = paste0("p = ", ..p.format..))
  #                  aes(
  # label=ifelse(..p.format.. == 1e-04, "p<0.001", "Other")
  )

# cart1$`CRP Pre-Leukapheresis`[cart1$`CRP Pre-Leukapheresis`=="<0.03"] <- 0.07
# cart1$`CRP Pre-Leukapheresis` <- as.numeric(cart1$`CRP Pre-Leukapheresis`)
# cart1$`CRP day +14`[cart1$`CRP day +14`=="<0.03"] <- 0.07
# cart1$`CRP day +14` <- as.numeric(cart1$`CRP day +14`)
# cart1$`CRP day +21`[cart1$`CRP day +21`=="<0.03"] <- 0.07
# cart1$`CRP day +21` <- as.numeric(cart1$`CRP day +21`)
# cart1$`CRP day +30`[cart1$`CRP day +30`=="<0.03"] <- 0.07
# cart1$`CRP day +30` <- as.numeric(cart1$`CRP day +30`)
CRP <- fig_dat %>% 
  select(pt_identifier, starts_with("crp_"), -crp_score) %>% 
  pivot_longer(cols = -c(pt_identifier)) %>% 
  mutate(name = str_remove(name, "_k_ul|_k_u_l"),
         day = case_when(
           str_detect(name, "apheresis")            ~ "-28",
           str_detect(name, "pretreatment")         ~ "-28",
           str_detect(name, "day")                  ~ ((str_match(name, "([0-9]+)"))[,2])
         ), 
         day = case_when(
           day == 5                                 ~ "-5",
           TRUE                                     ~ day
         ),
         day = factor(day, levels = c("-28", "-5", "0", 
                                      "7", "14", "21", "30", "90", "180"))) %>% 
  ggplot(aes(x=day, y=value)) + 
  geom_boxplot() + 
  xlab("Days") + ylab("CRP represented with a log2 scale") + 
  theme_classic() + ggtitle("CRP") + 
  scale_y_continuous(trans = "log2") +
  stat_compare_means(label.x = 1.2
                     # aes(label = paste0("p = ", ..p.format..))
  #                  aes(
  # label=ifelse(..p.format.. == 1e-04, "p<0.001", "Other")
  )

(LDH) /
(Ferritin) /
(CRP)+
plot_annotation(tag_levels = "A")

# ggsave("Figure S1 Inflammatory markers after cilta-cel.pdf",
#        width = 6,
#        height = 10)
```

@@

(WBC_fig | ANC_fig | CD4_fig) /
  (Hb_fig | ALC_fig | CD8_fig) /
  (Plt_fig | IgG_fig | CD19_fig) +
  plot_annotation(tag_levels = "A")

# ggsave("Figure 2 Cellular and humoral immune reconstitution after cilta-cel.pdf",
#        width = 15, 
#        height = 8)
```
<br>

@@

c %>% filter(grade == "Grade 3+") %>% 
  ggplot(aes(x= day, 
             y= perc, 
             fill= name, 
             ))+
  geom_bar(stat = "identity",
           position=position_dodge(width=0.9))+
  geom_text(aes(label = paste0(round(perc, 0), "%"), y=perc-2), size = 3,
            position = position_dodge(width=0.9), vjust=-1.5
            )+

  scale_fill_brewer(palette = "Spectral")+
  ylim(0, 60)+
  labs(fill = NULL, x= NULL, y = "Percent")+
  theme_classic(base_size = 9)+
  theme(legend.position="bottom")

# ggsave("Figure 3 Cytopenias over time.pdf",
#        width = 7,
#        height = 4)

@@

#            font.x = c(12, "bold", "black"),
#            font.y = c(12, "bold", "black"),
#            font.legend = c(12, "black"),
#            font.tickslab = c(10, "bold", "black"),

@@

```{r violin plot}
a <- cilta %>%
  mutate(os_from_infusion_days = os_from_infusion_months * 30.417) %>% 
  select(pt_identifier, any_infection, any_sevinfection, date_of_infection, 
         time_from_infusion_to_infection_days, infection_type_bacterial_viral_fungal_parasitic,
         infection_type_cat) %>% 
  mutate(any_sevinfection = case_when(
    any_sevinfection == "Yes"           ~ "Severe"
  )) %>% 
  mutate(any_infection = case_when(
    any_sevinfection == "Severe"        ~ NA_character_,
    any_infection == "Yes"              ~ "Not severe"
  )) %>% 
  pivot_longer(cols = c(any_infection, any_sevinfection), 
               names_to = "Infection", 
               values_to = "Infection severity") %>% 
  drop_na(`Infection severity`) %>% 
  mutate(infection_type_cat = str_replace(infection_type_cat, " \\+ ", " and ")) %>% 
  separate_wider_delim(cols = infection_type_cat, delim = " and ",
                       names = c("infection_type_cat1", "infection_type_cat2"), 
                       too_few = "align_start", too_many = "merge", 
                       cols_remove = TRUE) %>% 
  pivot_longer(cols = c(infection_type_cat1, infection_type_cat2), 
               names_to = NULL, 
               values_to = "Infection categories") %>% 
  drop_na(`Infection categories`) %>% 
  ggplot(aes(x = infection_type_bacterial_viral_fungal_parasitic, 
             y = time_from_infusion_to_infection_days))+
  geom_violin()+
  geom_jitter(aes(color = `Infection severity`), width = 0.2)+
  # geom_point(aes(color = `Infection severity`), position = "jitter")
  labs(x = NULL, y = "Infection onset time (days)")+
  scale_color_manual(values = c("black", "red"))+
  scale_y_continuous(expand = c(0, 5), limits = c(0, 400))+
  theme(axis.text.x = element_text(angle = 45, 
                                   hjust = 1#,
                                   # vjust = 0.5
                                   ))

b <- cilta %>%
  mutate(os_from_infusion_days = os_from_infusion_months * 30.417) %>% 
  select(pt_identifier, any_infection, any_sevinfection, date_of_infection, 
         time_from_infusion_to_infection_days,
         infection_type_cat) %>% 
  mutate(any_sevinfection = case_when(
    any_sevinfection == "Yes"           ~ "Severe"
  )) %>% 
  mutate(any_infection = case_when(
    any_sevinfection == "Severe"        ~ NA_character_,
    any_infection == "Yes"              ~ "Not severe"
  )) %>% 
  pivot_longer(cols = c(any_infection, any_sevinfection), 
               names_to = "Infection", 
               values_to = "Infection severity") %>% 
  drop_na(`Infection severity`) %>% 
  mutate(infection_type_cat = str_replace(infection_type_cat, "and Respiratory infection", "and Respiratory infections")) %>% 
  mutate(infection_type_cat = str_replace(infection_type_cat, " \\+ ", " and ")) %>% 
  separate_wider_delim(cols = infection_type_cat, delim = " and ",
                       names = c("infection_type_cat1", "infection_type_cat2"), 
                       too_few = "align_start", too_many = "merge", 
                       cols_remove = TRUE) %>% 
  pivot_longer(cols = c(infection_type_cat1, infection_type_cat2), 
               names_to = NULL, 
               values_to = "Infection categories") %>% 
  drop_na(`Infection categories`) %>% 
  ggplot(aes(x = `Infection categories`, 
             y = time_from_infusion_to_infection_days))+
  geom_violin()+
  geom_jitter(aes(color = `Infection severity`), width = 0.2)+
  # geom_point(aes(color = `Infection severity`), position = "jitter")
  labs(x = NULL, y = "Infection onset time (days)")+
  scale_color_manual(values = c("black", "red"))+
  scale_y_continuous(expand = c(0, 5), limits = c(0, 400))+
  # coord_flip()
  theme(axis.text.x = element_text(angle = 45, 
                                   hjust = 1#,
                                   # vjust = 0.5
                                   ))

c <- cilta %>%
  mutate(os_from_infusion_days = os_from_infusion_months * 30.417) %>%
  filter(infection_type_bacterial_viral_fungal_parasitic == "Viral") %>%
  select(pt_identifier, any_infection, any_sevinfection, date_of_infection,
         time_from_infusion_to_infection_days,
         viral_category) %>%
  mutate(any_sevinfection = case_when(
    any_sevinfection == "Yes"           ~ "Severe"
  )) %>%
  mutate(any_infection = case_when(
    any_sevinfection == "Severe"        ~ NA_character_,
    any_infection == "Yes"              ~ "Not severe"
  )) %>%
  pivot_longer(cols = c(any_infection, any_sevinfection),
               names_to = "Infection",
               values_to = "Infection severity") %>%
  drop_na(`Infection severity`) %>%
  mutate(viral_category = str_replace(viral_category, ", ", " And ")) %>% 
  mutate(viral_category = str_replace(viral_category, "Rhinovius", "Rhinovirus")) %>% 
  mutate(viral_category = str_replace(viral_category, "parainfluenza", "Parainfluenza")) %>% 
  mutate(viral_category = str_replace(viral_category, "Metapneurmovirus", "Metapneumovirus")) %>% 
  mutate(viral_category = str_remove(viral_category, "\\? ")) %>% 
  separate_wider_delim(cols = viral_category, delim = " And ",
                       names = c("viral_category1", "viral_category2"), 
                       too_few = "align_start", too_many = "merge", 
                       cols_remove = FALSE) %>% 
  pivot_longer(cols = c(viral_category1, viral_category2), 
               names_to = NULL, 
               values_to = "Viral categories") %>% 
  drop_na(`Viral categories`) %>% 
  ggplot(aes(x = `Viral categories`,
             y = time_from_infusion_to_infection_days))+
  geom_violin()+
  geom_jitter(aes(color = `Infection severity`), width = 0.2)+
  labs(x = NULL, y = "Infection onset time (days)")+
  scale_color_manual(values = c("black", "red"))+
  scale_y_continuous(expand = c(0, 5), limits = c(0, 400))+
  # coord_flip()
  theme(axis.text.x = element_text(angle = 45, 
                                   hjust = 1#,
                                   # vjust = 0.5
                                   ))

a /
  b /
  c +
  plot_annotation(tag_levels = "A")

# ggsave("Figure 4 Infection density.pdf",
#        width = 7,
#        height = 10)

@@

```{r alluvial combine, fig.height=12}
(alluvial_A) /
  (alluvial_B) + #/
  # (alluvial_C) +
  plot_annotation(tag_levels = "A")

# ggsave("Figure S3. Viral titers after cilta-cel.pdf",
#        width = 7,
#        height = 10)
```

@@

```{r alluvial day 180 combine, fig.height=12}
(alluvial_A) /
  (alluvial_B) + #/
  # (alluvial_C) 
  plot_annotation(tag_levels = "A")

# ggsave("Figure S3+day180 Viral titers after cilta-cel.pdf",
#        width = 7,
#        height = 10)
```

@@

ht_list <- Heatmap(df, name = " ", 
        rect_gp = gpar(col = "grey", lwd = 0.001), 
        column_title_side = "bottom",
        column_title = "Patients",
        show_column_names =FALSE,
        row_names_side = "left",
        row_names_gp = gpar(fontsize = 11),
        col = colors)
pdf("Figure S4 Pneumococcal titers after cilta-cel.pdf", 
    width = 8,
    height = 6)
draw(ht_list, heatmap_legend_side = "right")
dev.off()

@@

```{r forest plot 5}
forest_p <- 
  glm(gr3_cytopenia_90d ~ high_marrow_burden_50_percent + `gr3_cytopenia_-5d` +
        steroid_use_yes_no + number_of_prior_lines_of_therapy + baseline_ferritin_cat,
    data = mva_dat,
    family = "binomial") %>%
  tbl_regression(exponentiate = TRUE) %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  fill(OR, `95% CI`, .direction = "up") %>% 
  separate(`95% CI`, into = c("lower", "upper"), sep = ", ") %>% 
  filter(Characteristic %in% c("High marrow burden (≥50%)",
                 "gr3_cytopenia_-5d",
                 "baseline_ferritin_cat",
                 "Steroid Use",
                 "Number of prior lines of therapy") ) %>% 
  mutate_at(c("OR", "lower", "upper"), ~ as.numeric(.)) %>% 
  mutate(name= case_when(
    Characteristic == "High marrow burden (≥50%)"      ~ "High marrow burden (≥50%)",
    Characteristic == "gr3_cytopenia_-5d"      ~ "Grade ≥ 3 Cytopenia at Day -5",
    Characteristic == "Steroid Use"      ~ "Steroid use",
    Characteristic == "Number of prior lines of therapy"      ~ "Number of prior lines of therapy",
    Characteristic == "baseline_ferritin_cat"      ~ "Baseline ferritin"
  ))

# ggsave("Figure S2 Forest plot 5 variables.pdf", 
#        device = cairo_pdf,
#        width = 7,
#        height = 6)

@@

library(survival)
myplot <- ggsurvplot(survfit(Surv(pfs_from_infusion_months, pfs_event) ~ gr3_cytopenia_90d, 
                   data=surv_dat),
           # title = "PFS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(12, "bold", "black"),
           font.y = c(12, "bold", "black"),
           font.legend = c(12, "black"),
           font.tickslab = c(12, "bold", "black"),
           size = 1.5,

>>>>

```{r Figure 2. Inflammatory markers after cilta-cel, fig.height=12}
LDH <- fig_dat %>% 
  select(pt_identifier, starts_with("ldh_")) %>% 
  pivot_longer(cols = -c(pt_identifier)) %>% 
  mutate(name = str_remove(name, "_k_ul|_k_u_l"),
         day = case_when(
           str_detect(name, "apheresis")            ~ "-28",
           str_detect(name, "pretreatment")         ~ "-28",
           str_detect(name, "day")                  ~ ((str_match(name, "([0-9]+)"))[,2])
         ), 
         day = case_when(
           day == 5                                 ~ "-5",
           TRUE                                     ~ day
         ),
         day = factor(day, levels = c("-28", "-5", "0", 
                                      "7", "14", "21", "30", "90", "180"))) %>% 
  ggplot(aes(x=day, y=value)) + 
  geom_boxplot() + 
  xlab("Days") + ylab("LDH (log2 scale)") + 
  theme_classic() + ggtitle("LDH") + 
  scale_y_continuous(trans = "log2") +
  stat_compare_means(label.x = 1.2 , label.y.npc = 0.95,
                     size = 5
                     # aes(label = paste0("p = ", ..p.format..))
  #                  aes(
  # label=ifelse(..p.format.. == 1e-04, "p<0.001", "Other")
  )

# cart1$`Ferritin day +7`[cart1$`Ferritin day +7`==">33511"] <- /33511
# cart1$`Ferritin day +7` <- as.numeric(cart1$`Ferritin day +7`)
Ferritin <- fig_dat %>% 
  select(pt_identifier, starts_with("ferritin_"), -ferritin_score) %>% 
  pivot_longer(cols = -c(pt_identifier)) %>% 
  mutate(name = str_remove(name, "_k_ul|_k_u_l"),
         day = case_when(
           str_detect(name, "apheresis")            ~ "-28",
           str_detect(name, "pretreatment")         ~ "-28",
           str_detect(name, "day")                  ~ ((str_match(name, "([0-9]+)"))[,2])
         ), 
         day = case_when(
           day == 5                                 ~ "-5",
           TRUE                                     ~ day
         ),
         day = factor(day, levels = c("-28", "-5", "0", 
                                      "7", "14", "21", "30", "90", "180"))) %>% 
  ggplot(aes(x=day, y=value)) + 
  geom_boxplot() + 
  xlab("Days") + ylab("Ferritin (log2 scale)") + 
  theme_classic() + ggtitle("Ferritin") + 
  scale_y_continuous(trans = "log2") +
  stat_compare_means(label.x = 1.2 , label.y.npc = 0.95,
                     size = 5
                     # aes(label = paste0("p = ", ..p.format..))
  #                  aes(
  # label=ifelse(..p.format.. == 1e-04, "p<0.001", "Other")
  )

# cart1$`CRP Pre-Leukapheresis`[cart1$`CRP Pre-Leukapheresis`=="<0.03"] <- 0.07
# cart1$`CRP Pre-Leukapheresis` <- as.numeric(cart1$`CRP Pre-Leukapheresis`)
# cart1$`CRP day +14`[cart1$`CRP day +14`=="<0.03"] <- 0.07
# cart1$`CRP day +14` <- as.numeric(cart1$`CRP day +14`)
# cart1$`CRP day +21`[cart1$`CRP day +21`=="<0.03"] <- 0.07
# cart1$`CRP day +21` <- as.numeric(cart1$`CRP day +21`)
# cart1$`CRP day +30`[cart1$`CRP day +30`=="<0.03"] <- 0.07
# cart1$`CRP day +30` <- as.numeric(cart1$`CRP day +30`)
CRP <- fig_dat %>% 
  select(pt_identifier, starts_with("crp_"), -crp_score) %>% 
  pivot_longer(cols = -c(pt_identifier)) %>% 
  mutate(name = str_remove(name, "_k_ul|_k_u_l"),
         day = case_when(
           str_detect(name, "apheresis")            ~ "-28",
           str_detect(name, "pretreatment")         ~ "-28",
           str_detect(name, "day")                  ~ ((str_match(name, "([0-9]+)"))[,2])
         ), 
         day = case_when(
           day == 5                                 ~ "-5",
           TRUE                                     ~ day
         ),
         day = factor(day, levels = c("-28", "-5", "0", 
                                      "7", "14", "21", "30", "90", "180"))) %>% 
  ggplot(aes(x=day, y=value)) + 
  geom_boxplot() + 
  xlab("Days") + ylab("CRP (log2 scale)") + 
  theme_classic() + ggtitle("CRP") + 
  scale_y_continuous(trans = "log2") +
  stat_compare_means(label.x = 1.2, label.y.npc = 0.95,
                     size = 5
                     # aes(label = paste0("p = ", ..p.format..))
  #                  aes(
  # label=ifelse(..p.format.. == 1e-04, "p<0.001", "Other")
  )

(LDH) /
(Ferritin) /
(CRP)+
plot_annotation(tag_levels = "A") &
  theme(plot.tag = element_text(size = 17),
        text = element_text(size = 16))

# ggsave("Figure S1 Inflammatory markers after cilta-cel_03-12-25_300dpi.pdf",
#        width = 6,
#        height = 10)

ggsave("Figure S1 Inflammatory markers after cilta-cel_600dpi_1column_compress.tiff",
       dpi = 600, units = "in",
       width = 8,
       height = 11, compression = "lzw")

@@

(WBC_fig | ANC_fig | CD4_fig) /
  (Hb_fig | ALC_fig | CD8_fig) /
  (Plt_fig | IgG_fig | CD19_fig) +
  plot_annotation(tag_levels = "A") &
  theme(plot.tag = element_text(size = 15),
        axis.title = element_text(size = 13),
        axis.text.y = element_text(size = 11),
        axis.text.x = element_text(size = 8),
        legend.title = element_text(size = 13),
        legend.text = element_text(size = 11))

ggsave("Figure 2 Cellular and humoral immune reconstitution after cilta-cel_600dpi_2column.tiff",
       dpi = 600, units = "in",
       width = 16,
       height = 8)

# (WBC_fig | ANC_fig) /
#   (CD4_fig | Hb_fig) / 
#   (ALC_fig | CD8_fig) /
#   (Plt_fig | IgG_fig) / 
#   (CD19_fig | plot_spacer()) +
#   plot_annotation(tag_levels = "A") &
#   theme(plot.tag = element_text(size = 16),
#         axis.title = element_text(size = 16),
#         axis.text.y = element_text(size = 14),
#         axis.text.x = element_text(size = 13),
#         legend.title = element_text(size = 16),
#         legend.text = element_text(size = 14))
# 
# ggsave("Figure 2 Cellular and humoral immune reconstitution after cilta-cel_600dpi_2column_.jpeg",
#        dpi = 600, units = "in",
#        width = 16,
#        height = 13)

@@

c %>% filter(grade == "Grade 3+") %>% 
  ggplot(aes(x= day, 
             y= perc, 
             fill= name, 
             ))+
  geom_bar(stat = "identity",
           position=position_dodge(width=0.9))+
  geom_text(aes(label = paste0(round(perc, 0), "%"), y=perc-2), size = 4,
            position = position_dodge(width=0.9), vjust=-1.5
            )+

  scale_fill_brewer(palette = "Spectral")+
  ylim(0, 60)+
  labs(fill = NULL, x= NULL, y = "Percent")+
  theme_classic(base_size = 9)+
  theme(legend.position="bottom", text = element_text(size = 16))

ggsave("Figure 3 Cytopenias over time_600dpi_1column_compress.tiff",
       dpi = 600, units = "in",
       width = 8,
       height = 4, compression = "lzw")

c %>% filter(grade == "Grade 3+") %>% 
  ggplot(aes(x= day, 
             y= perc, 
             fill= name, 
             ))+
  geom_bar(stat = "identity",
           position=position_dodge(width=0.9))+
  geom_text(aes(label = paste0(round(perc, 0), "%"), y=perc-2), size = 7,
            position = position_dodge(width=0.9), vjust=-1.5
            )+

  scale_fill_brewer(palette = "Spectral")+
  ylim(0, 60)+
  labs(fill = NULL, x= NULL, y = "Percent")+
  theme_classic(base_size = 9)+
  theme(legend.position="bottom", text = element_text(size = 20))
ggsave("Figure 3 Cytopenias over time_600dpi_2column_compress.tiff",
       dpi = 600, units = "in",
       width = 16,
       height = 8, compression = "lzw")

@@

#            font.x = c(15, "bold", "black"),
#            font.y = c(15, "bold", "black"),
#            font.legend = c(14, "black"),
#            font.tickslab = c(12, "bold", "black"),

@@

```{r violin plot}
a <- cilta %>%
  mutate(os_from_infusion_days = os_from_infusion_months * 30.417) %>% 
  select(pt_identifier, any_infection, any_sevinfection, date_of_infection, 
         time_from_infusion_to_infection_days, infection_type_bacterial_viral_fungal_parasitic,
         infection_type_cat) %>% 
  mutate(any_sevinfection = case_when(
    any_sevinfection == "Yes"           ~ "Severe"
  )) %>% 
  mutate(any_infection = case_when(
    any_sevinfection == "Severe"        ~ NA_character_,
    any_infection == "Yes"              ~ "Not severe"
  )) %>% 
  pivot_longer(cols = c(any_infection, any_sevinfection), 
               names_to = "Infection", 
               values_to = "Infection severity") %>% 
  drop_na(`Infection severity`) %>% 
  mutate(infection_type_cat = str_replace(infection_type_cat, " \\+ ", " and ")) %>% 
  separate_wider_delim(cols = infection_type_cat, delim = " and ",
                       names = c("infection_type_cat1", "infection_type_cat2"), 
                       too_few = "align_start", too_many = "merge", 
                       cols_remove = TRUE) %>% 
  pivot_longer(cols = c(infection_type_cat1, infection_type_cat2), 
               names_to = NULL, 
               values_to = "Infection categories") %>% 
  drop_na(`Infection categories`) %>% 
  ggplot(aes(x = infection_type_bacterial_viral_fungal_parasitic, 
             y = time_from_infusion_to_infection_days))+
  geom_violin()+
  geom_jitter(aes(color = `Infection severity`), width = 0.2)+
  # geom_point(aes(color = `Infection severity`), position = "jitter")
  labs(x = NULL, y = "Infection onset (days)")+
  scale_color_manual(values = c("black", "red"))+
  scale_y_continuous(expand = c(0, 5), limits = c(0, 400))+
  theme(axis.text.x = element_text(angle = 45, 
                                   hjust = 1#,
                                   # vjust = 0.5
                                   ), 
        text = element_text(size = 15))

b <- cilta %>%
  mutate(os_from_infusion_days = os_from_infusion_months * 30.417) %>% 
  select(pt_identifier, any_infection, any_sevinfection, date_of_infection, 
         time_from_infusion_to_infection_days,
         infection_type_cat) %>% 
  mutate(any_sevinfection = case_when(
    any_sevinfection == "Yes"           ~ "Severe"
  )) %>% 
  mutate(any_infection = case_when(
    any_sevinfection == "Severe"        ~ NA_character_,
    any_infection == "Yes"              ~ "Not severe"
  )) %>% 
  pivot_longer(cols = c(any_infection, any_sevinfection), 
               names_to = "Infection", 
               values_to = "Infection severity") %>% 
  drop_na(`Infection severity`) %>% 
  mutate(infection_type_cat = str_replace(infection_type_cat, "and Respiratory infection", "and Respiratory infections")) %>% 
  mutate(infection_type_cat = str_replace(infection_type_cat, " \\+ ", " and ")) %>% 
  separate_wider_delim(cols = infection_type_cat, delim = " and ",
                       names = c("infection_type_cat1", "infection_type_cat2"), 
                       too_few = "align_start", too_many = "merge", 
                       cols_remove = TRUE) %>% 
  pivot_longer(cols = c(infection_type_cat1, infection_type_cat2), 
               names_to = NULL, 
               values_to = "Infection categories") %>% 
  drop_na(`Infection categories`) %>% 
  ggplot(aes(x = `Infection categories`, 
             y = time_from_infusion_to_infection_days))+
  geom_violin()+
  geom_jitter(aes(color = `Infection severity`), width = 0.2)+
  # geom_point(aes(color = `Infection severity`), position = "jitter")
  labs(x = NULL, y = "Infection onset (days)")+
  scale_color_manual(values = c("black", "red"))+
  scale_y_continuous(expand = c(0, 5), limits = c(0, 400))+
  # coord_flip()
  theme(axis.text.x = element_text(angle = 45, 
                                   hjust = 1#,
                                   # vjust = 0.5
                                   ), 
        text = element_text(size = 15))

c <- cilta %>%
  mutate(os_from_infusion_days = os_from_infusion_months * 30.417) %>%
  filter(infection_type_bacterial_viral_fungal_parasitic == "Viral") %>%
  select(pt_identifier, any_infection, any_sevinfection, date_of_infection,
         time_from_infusion_to_infection_days,
         viral_category) %>%
  mutate(any_sevinfection = case_when(
    any_sevinfection == "Yes"           ~ "Severe"
  )) %>%
  mutate(any_infection = case_when(
    any_sevinfection == "Severe"        ~ NA_character_,
    any_infection == "Yes"              ~ "Not severe"
  )) %>%
  pivot_longer(cols = c(any_infection, any_sevinfection),
               names_to = "Infection",
               values_to = "Infection severity") %>%
  drop_na(`Infection severity`) %>%
  mutate(viral_category = str_replace(viral_category, ", ", " And ")) %>% 
  mutate(viral_category = str_replace(viral_category, "Rhinovius", "Rhinovirus")) %>% 
  mutate(viral_category = str_replace(viral_category, "parainfluenza", "Parainfluenza")) %>% 
  mutate(viral_category = str_replace(viral_category, "Metapneurmovirus", "Metapneumovirus")) %>% 
  mutate(viral_category = str_remove(viral_category, "\\? ")) %>% 
  separate_wider_delim(cols = viral_category, delim = " And ",
                       names = c("viral_category1", "viral_category2"), 
                       too_few = "align_start", too_many = "merge", 
                       cols_remove = FALSE) %>% 
  pivot_longer(cols = c(viral_category1, viral_category2), 
               names_to = NULL, 
               values_to = "Viral categories") %>% 
  drop_na(`Viral categories`) %>% 
  ggplot(aes(x = `Viral categories`,
             y = time_from_infusion_to_infection_days))+
  geom_violin()+
  geom_jitter(aes(color = `Infection severity`), width = 0.2)+
  labs(x = NULL, y = "Infection onset (days)")+
  scale_color_manual(values = c("black", "red"))+
  scale_y_continuous(expand = c(0, 5), limits = c(0, 400))+
  # coord_flip()
  theme(axis.text.x = element_text(angle = 45, 
                                   hjust = 1#,
                                   # vjust = 0.5
                                   ), 
        text = element_text(size = 15))

a /
  b /
  c +
  plot_annotation(tag_levels = "A")&
  theme(plot.tag = element_text(size = 15),
        axis.title = element_text(size = 15),
        axis.text = element_text(size = 13),
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15))

ggsave("Figure 4 Infection density_600dpi_1column_compress.tiff",
       dpi = 600, units = "in",
       width = 8,
       height = 11, compression = "lzw")

@@

```{r alluvial combine, fig.height=12}
(alluvial_A) /
  (alluvial_B) + #/
  # (alluvial_C) +
  plot_annotation(tag_levels = "A")&
  theme(text = element_text(size = 15)#,
        # plot.tag = element_text(size = 15)
        )

ggsave("Figure S3. Viral titers after cilta-cel_600dpi_1column.tiff",
       dpi = 600, units = "in",
       width = 8,
       height = 10, compression = "lzw")
```

@@

```{r alluvial day 180 combine, fig.height=12}
(alluvial_A) /
  (alluvial_B) + #/
  # (alluvial_C) 
  plot_annotation(tag_levels = "A")&
  theme(text = element_text(size = 15))

ggsave("Figure S3+day180 Viral titers after cilta-cel_600dpi_1column_compress.tiff",
       dpi = 600, units = "in",
       width = 8,
       height = 10, compression = "lzw")
```

@@

ht_list <- Heatmap(df, name = " ", 
        rect_gp = gpar(col = "grey", lwd = 0.001), 
        column_title_side = "bottom",
        column_title = "Patients",
        show_column_names =FALSE,
        row_names_side = "left",
        row_names_gp = gpar(fontsize = 14),
        heatmap_legend_param = list(labels_gp = gpar(fontsize = 14)),
        col = colors)
ht_list
# pdf("Figure S4 Pneumococcal titers after cilta-cel.pdf", 
#     width = 8,
#     height = 6)
# draw(ht_list, heatmap_legend_side = "right")
# dev.off()

tiff("Figure S4 Pneumococcal titers after cilta-cel_600dpi_1column.tiff", 
     res = 600, units = "in",
    width = 8,
    height = 5)
ht_list
# draw(ht_list, heatmap_legend_side = "right")
dev.off()

ragg::agg_tiff("ht_list.tiff", width = 8,
    height = 5, units = "in", res = 600, compression = "lzw")
ht_list
dev.off()

@@

```{r forest plot 5}
forest_p <- 
  glm(gr3_cytopenia_90d ~ high_marrow_burden_50_percent + `gr3_cytopenia_-5d` +
        steroid_use_yes_no + number_of_prior_lines_of_therapy + baseline_ferritin_cat,
    data = mva_dat,
    family = "binomial") %>%
  tbl_regression(exponentiate = TRUE) %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  fill(OR, `95% CI`, .direction = "up") %>% 
  separate(`95% CI`, into = c("lower", "upper"), sep = ", ") %>% 
  filter(Characteristic %in% c("High marrow burden (≥50%)",
                 "gr3_cytopenia_-5d",
                 "baseline_ferritin_cat",
                 "Steroid Use",
                 "Number of prior lines of therapy") ) %>% 
  mutate_at(c("OR", "lower", "upper"), ~ as.numeric(.)) %>% 
  mutate(name= case_when(
    Characteristic == "High marrow burden (≥50%)"      ~ "High marrow \nburden (≥50%)",
    Characteristic == "gr3_cytopenia_-5d"      ~ "Grade ≥ 3 Cytopenia \nat Day -5",
    Characteristic == "Steroid Use"      ~ "Steroid use",
    Characteristic == "Number of prior lines of therapy"      ~ "Number of prior \nlines of therapy",
    Characteristic == "baseline_ferritin_cat"      ~ "Baseline ferritin"
  ))

ggplot(data=forest_p, aes(y=name, x=OR, xmin=lower, xmax=upper)) +
  geom_point() + 
  geom_errorbarh(height=.1) +
  geom_vline(xintercept=1, color='black', linetype='dashed', alpha=.5) +
  theme_classic()+
  scale_x_log10(breaks = c(0, 0.25, 0.5, 1, 2.5, 5, 10, 40))+
  labs(y="") %>% 
  theme(text = element_text(size = 15),
        axis.title.y = element_blank())

ggsave("Figure S2 Forest plot 5 variables_600dpi_1column_wraplabel_compress.tiff",
       dpi = 600, units = "in",
       width = 8,
       height = 4, compression = "lzw"#6
       )

@@

library(survival)
myplot <- ggsurvplot(survfit(Surv(pfs_from_infusion_months, pfs_event) ~ gr3_cytopenia_90d, 
                   data=surv_dat),
           # title = "PFS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(15, "bold", "black"),
           font.y = c(15, "bold", "black"),
           font.legend = c(14, "black"),
           font.tickslab = c(12, "bold", "black"),
           size = 1.5,

           xlab = "Time (months)",
           ylab = "PFS (probability)",
           legend = "top",
           legend.title = "≥ Grade 3 cytopenia at D90",
           legend.labs = c("No", "Yes"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE,
           risk.table = TRUE, risk.table.y.text = TRUE,
           tables.theme = theme_survminer(#base_size = 5,
                                          font.main = c(14, "bold", "black"),
                                          # font.x = c(10, "bold", "black"),
                                          # font.y = c(16, "bold", "transparent"),
                                          # font.tickslab = c(19, "bold", "black")
                                          )
) %++% guides(colour = guide_legend(nrow = 1))
risk.table.ylab <- "≥ Grade 3 \ncytopenia at D90"
myplot$table <- myplot$table + labs(y = risk.table.ylab)
myplot
